---
title: "Developing Data Product-Week2-R Markdown and Leaflet"
author: "MassaBrasil"
date: "3rd Januar,  2018"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Food adventure in São Paulo, Brazil - suggestions

When having chance to spend at least 48 hours layover in Sao Paulo (Brazil), here I enlist some suggestions to get acquainted with a blink of its vast and varied gastronomy.

I apologize in advance for mentioning just very few options while there are tons of equally interesting options varying from local and the most representative nation communities that composes its population.

This was written motivated by the chance to share to colleagues from abroad some information of a city they probably still don´t know and could be curious about (even the experience of the author is very, very limited! )

Food uses to be a way to know and get connected to people and their environment.

As one of largest city in South America, metropolitan food markets, popular restaurants and bars are good way to blend with locals and feel the pulse of the city.

(check before for holidays, as they can be closed). 

### (1) CEAGESP, to eat pastel

When you have available in agenda Saturday or Sunday from 6am to 12pm, go to CEAGESP, kind of city food market - there you can find some interesting local/regional foods and traits - stroll from stand to stand trying (for free) bites of fresh fruits - different banana types - gold (ouro), apple (banana maçã, pronounce mah-sahn), silver (banana prata); or pear orange  (laranja pera); 

If you enjoy sweetness, you must meet and try these brazilian fruit: 

- banana ( maçã, prata R$ 5,00 1 kilo)
- jaca (jah-ka) (R$ 10,00 a tray with 12 pieces peeled) 
- atemóia (ah-teh-mowl-yeah) 
- Mamao (giant papaya)
- Abacate (giant avocado)
- melancia (water melon)

Green coconut water opened on the spot. Changing to a typical trait of Sao Paulo city, try pastel (deep fried thin dought filled of ground meat, cheese, ground chicken, special:egg, cheese,meat - the must are the dressings - on the stand 'Miyazato', try pastel de carne with the green dressing!!! if you like strong pepper, try the red one; see https://pt.foursquare.com/v/pastel-miyasato/4fc254aee4b021b6e0286c46/photos ). (R$ 5,00 each, 70g, 8cm X 15cm)

If you go to stand 'Miyazato', at its side you can find a truck extracting/selling sugar cane juice (caldo de cana) in large plastic cup with some lime juice - it´s worth to try fresh & iced in the summer!!!  (R$ 5,00 300ml cup) 

### (2) Churrascaria Fogo de Chão 

'Fogo de Chão' - means 'bonfire in the ground', where gauchos (those natives in region from South Brazil, Uruguay, and part of Argentina) set large part of cattle to grill slowly.  

If you can afford and like to eat grilled meat, it is a good chance to enjoy large  variety of meat cuts and their respective distinct flavors, accompanied by large variety of fresh greens, palm heart, preserved cheese and olive.

You pay a fixed fee (R$ 250,00 per person) to eat as much as you can - popular meat cut in Brazil is named 'picanha' (pee-kahn-nya, i.e. sirloin) , but there are a number of other cuts (ribs, rump steal, flank steak,hump, top sirloin cap), and other options: chicken heart, sausage. (see http://www.fogodechao.com.br )

You can harmonize with wines - some brazilian wine labels: Aurora, Miolo, Salton, Casa Valduga, Almadén.

Remember to be stood up for desserts - Milk flan, milk caramel, fruit salad, - my best choice is blended papaya with cream ice cream with cassis liqueur generously poured on the  top! (refreshing, digestive).

### (3) Restaurant Tenko

If you are keen to eat oriental food - steamed/boiled dumpling or hand made noodles on the broth enriched with vegetables, meat and seafood in a reasonably short budget, this is an excellent suggestion!

In two or three, you can have a confortant meal - starting with appetizer - 'joelho de porco' (sliced pork knee), 'prato misto' (sliced tofu, bovine stomach, muscle), 'mandu' (boiled meat dumpling filled with mix of nira leaves and ground meat) and dressing made in your bolw (a spoonful of vinegar, another of sesame oil, another of soy sauce and tea spoon of home made red pepper sauce - you will get addicted!! - see https://www.tripadvisor.com.br/Restaurant_Review-g303631-d5395217-Reviews-Tenko-Sao_Paulo_State_of_Sao_Paulo.html ) 

Main meal - suggestion is Chanpon Bowl (order it with pepper, otherwise you will taste a kind of sweet broth, I myself don´t like that way).

Some dishes are original from Korea, although restaurant is run by sympathetic Taiwanese brothers.

For drinking, if you still didn´t taste Guaraná (gu-a-rah-naah), you must - it is a soft drink made of guaraná fruit (actually very bitter, told that natives use it as natural stimulant), very popular in Brazil.

For beer, there are some popular brands among locals - just mentioning some of them: Original, SerraMalte, Itaipava, Petropolis (I don´t like Kaiser).

(My choices are SerraMalte and Original).

## Sao Paulo city - map and spots

## Report date

```{r, echo=FALSE }

date()

```

```{r, echo=FALSE }

library(leaflet)

my_map <- leaflet() %>%
  addTiles()

my_map <-  my_map %>%

    addMarkers(lat=-23.5371994,lng=-46.738026,
             popup="(1) CEAGESP - banca pastel Miyasato")

  
my_map <-  my_map %>%

    addMarkers(lat=-23.5988153,lng=-46.6878927,
             popup="(2) Churrascaria Fogo de Chão")

my_map <-  my_map %>%

    addMarkers(lat=-23.5555902,lng=-46.6338032,
             popup="(3) Restaurante Tenko")

my_map
```


## Suggestion for stay and transportation

A practical way to move around the city is to use Uber driver service (payable in credit card - with chip only)

Stay in a hotel near subway station of lines yellow (linha 4) or green (linha 2) - train ticket is %$ 3,80 (less than 1,30 US dollar, no matter the distance).


Pre-paid mobile chip: you can buy chip with expiry date in one week with 2GB mobile data plan with 60 minutes of local calls. 

Economic hotel brand available: Mercury, Ibis.

## Exchange rate

US$ 1 = ~ R$ 3,10 real (3/jan/2018)


## Do and dont's

Dont's:

- show off mobile phone, wallet, jewery, cash in public

- approach odd grouping of people (begger, drug addicted)

- go far in suburbs - security surveillance and police patrolling uses to be not sufficient.

- go far alone without plan (even locals can easily get in trouble that way)

Do:

- wear low profile clothes as possible.

- always let someone know where you go and the time you see that will be back, register each other in APPs like Friends that shows your location.

- before you go around, get written and keep with  yourself address of your stay place, phone numbers of acquaintances, consulate office, tourist support police station. 

- if you can afford longer stays, use Sao Paulo as base to travel to other attraction cities in Brazil and South America - e.g. Foz do Iguaçu (Park of birds, Iguaçu Dam hidroelectric plant, Paraguai and Argentina borders), Buenos Aires and tango shows, preserved architecture, parrilla and wines, dulce de leche (milk sweet). 

