---
title: "Developing Data Product-Week2-R Markdown and Leaflet"
author: "MassaBrasil"
date: "3rd Januar,  2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Food adventure in São Paulo, Brazil - suggestions

When have chance to spend some at least half a day layover in Sao Paulo (Brazil) I have some suggestions as spots that you can enjoy.

As largest city in South America, metropolitan food markets and some popular restaurants and bars are good way to blend with and feel the mood among locals trying to exercise some Portuguese.

(check before for holidays, as they can be closed). 

### (1) CEAGESP :

When you have available in agenda Saturday or Sunday from 6am to 12pm, go to CEAGESP, kind of city food market - there you can find some interesting local/regional foods and traits - stroll from stand to stand trying (for free) bites of fresh fruits - different banana types - gold (banana ouro), 'apple-ish' (ban.. maçã, pronounce mah-sahn), 'silver-ish' (ban.. prata), orange types 'pear-ish' (laranja pera); 

focusing in sweety brazilian fruits - jaca (jah-ka), green coconut water opened on the spot. Changing to a typical trait of Sao Paulo city, try pastel (deep fried thin dought filled of ground meat, cheese, ground chicken, special:egg, cheese,meat - the must are the dressings - on the stand 'Miyazato', try pastel de carne with the green dressing!!! if you like strong pepper, try the red one; it will be like boomerang, it´s highly possible that your pepper awareness be activated twice hahah !!). 

If you go to stand 'Miyazato', at its side you can find a truck extracting/selling sugar cane juice (caldo de cana) in large plastic cup with some lime juice - it´s worth to try fresh & iced in the summer!!! 

### (2) Churrascaria Fogo de Chão 

'Fogo de Chão' - means 'bonfire in the ground', where gauchos (those natives in region from South Brazil, Uruguay, and part of Argentina) set cattle cut piece in slow grilling for meals.

If you can afford and like to eat grilled meat, it is a good chance to enjoy large  variety of meat cuts and distinct flavors, accompanied of also large variety of fresh greens, palm heart, preserved cheese. 

You can harmonize with wines from South America (Argentinian, Chilean, Brazilian) and other regions.

Remember to be stood up for desserts - Milk flan, milk caramel, fruit salad, - my best choice is blended papaya with cream ice cream with cassis liqueur generously poured on the  top! (refreshing, digestive).

### (3) Restaurant Tenko

If you are keen to eat oriental food - steamed/boiled dumpling or hand made noodles on the broth enriched with vegetables, meat and seafood in a reasonably short budget, this is an excellent suggestion!

In two or three, you can have a confortant meal - starting with appetizer - 'joelho de porco' (sliced pork knee), 'prato misto' (sliced tofu, bovine stomach, muscle), 'mandu' (boiled meat dumpling filled with mix of nira leaves and ground meat) and dressing made in your bolw (a spoonful of vinegar, another of sesame oil, another of soy sauce and tea spoon of home made red pepper sauce - you will get addicted!! )

Last round - suggestion is Chanpon Bowl (with peper sprinkled, otherwise you will taste a kind of sweet broth, I myself don´t like).

Some dishes are original from Korea, although restaurant is run by sympathetic Taiwanese brothers.

For drinking, if you still didn´t taste Guaraná (gu-a-ra-naah), you must - it is a soft drink made of guaraná fruit (actually very bitter, told that natives use it as natural stimulant), very popular in Brazil.

For beer, there are some popular brands among locals - just mentioning some of them: Original, SerraMalte, Itaipava, Petropolis (I don´t like Kaiser).

(My choices are SerraMalte and Original).

## Sao Paulo city - map and spots

## Report date

```{r, echo=FALSE }
date()
```

```{r, echo=FALSE}

library(leaflet)

my_map <- leaflet() %>%
  addTiles()

my_map <-  my_map %>%

    addMarkers(lat=-23.5371994,lng=-46.738026,
             popup="(1) CEAGESP - city food market")

  
my_map <-  my_map %>%

    addMarkers(lat=-23.5988153,lng=-46.6878927,
             popup="(2) Churrascaria Fogo de Chão")

my_map <-  my_map %>%

    addMarkers(lat=-23.5555902,lng=-46.6338032,
             popup="(3) Restaurante Tenko")

my_map
```
## Suggestion for stay and transportation

A practical way to move around the city is to use Uber driver service (payable in credit card - with chip only)

Stay in a hotel near subway station of lines yellow (linha 4) or green (linha 2) - train ticket is %$ 3,80 (less than 1,30 US dollar, no matter the distance).

Avoid going far in suburbs - security surveillance and police patrol uses to be weak.

Pre-paid mobile chip: you can buy chip with expiry date in one week with 2GB mobile data plan with 60 minutes of local calls. 

Economic hotel brand available: Mercury, Ibis.


## Do and dont's

Dont's:

- show off mobile phone, wallet, jewery, cash in public

- approach odd grouping of people (begger, drug addicted)

- go far alone without plan (even locals can easily get in trouble that way)

Do:

- wear low profile clothes as possible.

- always let someone know where you go and the time you see that will be back, register each other in APPs like Friends that shows your location.

- before you go around, get written and keep with  yourself address of your stay place, phone numbers of acquaintances, consulate office, tourist support police station. 



